DeconvOptim.jl - Signal Deconvolution with Julia

### 2024-02-10 paper/paper.tex
Fix style of BenchmarkTools.jl [skip ci]

\subsection{Regularizer}
    The regularizer is an additional part in the total loss to add some additional priors like sparsity and smoothness.
    Most real samples are smooth over large regions and such regularizers enhance the quality of the reconstruction.
    In our toolbox we currently implement several regularizer like (smoothed) Total Variation, Good's roughness \cite{Verveer:98}, \cite{Good:71} and Tikhonov. 
    \subsubsection{Total Variation as example}
        As the name suggests, Total Variation tries to penalize variation in the image intensity. Therefore it sums up the gradient strength at each point
        of the image:
        \begin{equation}
            \text{Reg}(S(\mathbf r)) = \sum_r  |(\nabla S)(\mathbf r)|
        \end{equation}
        Since we look at the magnitude of the gradient strength, this regularizer is anisotropic.
        In 2D TV is defined like: 
        \begin{equation}
        \begin{split}
            \text{Reg}(S(\mathbf r)) = \sum_{x,y} \big[& |S(x + 1, y) - S(x, y)|^2 \\[-0.4cm] 
                                                & + |S(x, y + 1) - S(x, y)|^2\big]^{\frac12}
        \end{split}
        \end{equation}
        In many frameworks, such a regularizer is implemented via functions like \lstinline{circshift}. 
        However, such approaches create often several copies of the data. 
        We currently use \verb|Tullio.jl|\cite{michael_abbott_2021_5047410} to create efficient functions 
        calculating the regularizer and the gradient. For simple expressions
        such as below, \verb|Tullio.jl| registers an analytical gradient and therefore allows to apply the same efficient mechanisms 
        to the gradient calculation which have been used for the regularizer evaluation itself.
        A (smoothed) Total Variation with \verb|Tullio.jl| is defined here:
        \begin{lstlisting}[language = Julia]
function total_variation(arr, ϵ=eltype(arr)(1e-8))
    @tullio r = sqrt(ϵ + 
                abs2(arr[i,j] - arr[i+1,j]) +
                abs2(arr[i,j] - arr[i,j+1]))
end
        \end{lstlisting}
        \lstinline{ϵ} is needed for regions where \lstinline{arr == 0} because otherwise the gradient returns infinite values.
        Note, that definition just demonstrates how the regularizer can be written down.
        In our toolbox we allow for much more options. Since \verb|Tullio.jl| cannot handle generic multi-dimensional data yet
        we create regularizers which can vary in step size, dimensionality and
        different weighting in dimensions via Julia's metaprogramming capability.
        A call like 
        \begin{lstlisting}[language = Julia]
julia> using DeconvOptim

@@

\section{Experiments}
    In this section we show some experiments and compare parts of the software to other solutions.
All experiments were executed on Ubuntu 20.04 using a AMD Ryzen 5 5600X 6-Core processor (12 threads) with \SI{32}{GB} DDR4 RAM and Julia 1.6.2.
    If possible, all threads were used.
    As GPU accelerator we used a GeForce RTX 2060 SUPER with \SI{8}{GB} memory and CUDA 11.3 and CUDA.jl 3.3.1.
    Our experiments were done in Julia 1.6.2 under the use of BenchmarkTools.jl\cite{BenchmarkTools.jl-2016}.

>>>>

\subsection{Regularizer}
    The regularizer is an additional part in the total loss to add some additional priors like sparsity and smoothness.
    Most real samples are smooth over large regions and such regularizers enhance the quality of the reconstruction.
    In our toolbox we currently implement several regularizer like (smoothed) Total Variation, Good's roughness \cite{Verveer:98}, \cite{Good:71} and Tikhonov. 
    \subsubsection{Total Variation as example}
        As the name suggests, Total Variation tries to penalize variation in the image intensity. Therefore it sums up the gradient strength at each point
        of the image:
        \begin{equation}
            \text{Reg}(S(\mathbf r)) = \sum_r  |(\nabla S)(\mathbf r)|
        \end{equation}
        Since we look at the magnitude of the gradient strength, this regularizer is anisotropic.
        In 2D TV is defined like: 
        \begin{equation}
        \begin{split}
            \text{Reg}(S(\mathbf r)) = \sum_{x,y} \big[& |S(x + 1, y) - S(x, y)|^2 \\[-0.4cm] 
                                                & + |S(x, y + 1) - S(x, y)|^2\big]^{\frac12}
        \end{split}
        \end{equation}
        In many frameworks, such a regularizer is implemented via functions like \lstinline{circshift}. 
        \begin{lstlisting}[language = Julia, caption={Smoothed Total Variation \label{algo1}}]
function total_variation(arr, ϵ=eltype(arr)(1e-8))
    @tullio r = sqrt(ϵ + 
                abs2(arr[i,j] - arr[i+1,j]) +
                abs2(arr[i,j] - arr[i,j+1]))
end
        \end{lstlisting}
        However, such approaches create often several copies of the data. 
        We currently use \verb|Tullio.jl| \cite{michael_abbott_2021_5047410} to create efficient functions 
        calculating the regularizer and the gradient. For simple expressions
        such as below, \verb|Tullio.jl| registers an analytical gradient and therefore allows to apply the same efficient mechanisms 
        to the gradient calculation which have been used for the regularizer evaluation itself.
        A (smoothed) Total Variation with \verb|Tullio.jl| is defined in \autoref{algo1}.
        \lstinline{ϵ} is needed for regions where \lstinline{arr == 0} because otherwise the gradient returns infinite values.
        Note, that definition just demonstrates how the regularizer can be written down.
        In our toolbox we allow for much more options. Since \verb|Tullio.jl| cannot handle generic multi-dimensional data yet
        we create regularizers which can vary in step size, dimensionality and
        different weighting in dimensions via Julia's metaprogramming capability.

        A call like 
        \begin{lstlisting}[language = Julia]
julia> using DeconvOptim

@@

\section{Experiments}
    In this section we show some experiments and compare parts of the software to other solutions.
All experiments were executed on Ubuntu 20.04 using a AMD Ryzen 5 5600X 6-Core processor (12 threads) with \SI{32}{GB} DDR4 RAM and Julia 1.6.2.
    If possible, all threads were used.
    As GPU accelerator we used a GeForce RTX 2060 SUPER with \SI{8}{GB} memory and CUDA 11.3 and CUDA.jl 3.3.1.
    Our experiments were done in Julia 1.6.2 under the use of \texttt{BenchmarkTools.jl}\cite{BenchmarkTools.jl-2016}.
